### 2021-04-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

RSA implementations blinding the data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  \ctool{} identify several functions that are vulnerable to side-channel attacks. We are interested if those leaked functions are fixed in the updated version.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity. We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool. \tool{} can tell which line in the source code actually leaks the information. So it is possible that one function has several leakage sites. Suppose the function has two leakages sites and they leak $a$ and $b$ bits respectively. We use the set $(a, b)$ to represent the result of \tool{}.

>>>>

RSA implementations are blinding the data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  \ctool{} identify several functions that are vulnerable to side-channel attacks. We are interested if those leaked functions are fixed in the updated version.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity. We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool. \tool{} can tell which line in the source code actually leaks the information. So it is possible that one function has several leakage sites. Suppose the function has two leakages sites, and they leak $a$ and $b$ bits, respectively. We use the set $(a, b)$ to represent the result of \tool{}.
